Enforcing Boundaries: China's Overseas NGO Law and Operational Constraints for Global Civil Society

### 2024-01-23 manuscript/manuscript.qmd
add citations

By focusing on INGO operational space in China, we provide a unique empirical view into the *de facto* regulatory environment for foreign civil society in an authoritarian state. General indexes of civil society openness---such as the core civil society index from the Varieties of Democracy project [@LianMurdie:2023; @ChaudhryHeiss:2022]---capture the regulatory environment for civil society more broadly, but do not reflect the specific implementation of laws for INGOs. Existing literature on China's ONGO Law mostly discussed the *de jure* legislation around the time when the law was implemented (to add reference) or reports case studies of how selected INGOs navigated the new legal framework shortly after the law took effect (to add reference). This paper is the first large N study of all registered INGOs and expands the time frame to the five years enforcement of the ONGO Law, providing insights for both scholars and practitioners on how the operational space of INGOs varies by issue areas and factors such as local connections.

>>>>

By focusing on INGO operational space in China, we provide a unique empirical view into the *de facto* regulatory environment for foreign civil society in an authoritarian state. General indexes of civil society openness---such as the core civil society index from the Varieties of Democracy project [@LianMurdie:2023; @ChaudhryHeiss:2022]---capture the regulatory environment for civil society more broadly, but do not reflect the specific implementation of laws for INGOs. Existing literature on China's ONGO Law mostly discussed the *de jure* legislation around the time when the law was implemented [Feng:2017; TeetsHsu:2016] or reports case studies of how selected INGOs navigated the new legal framework shortly after the law took effect [@Li:2020; WuNie:2021]. This paper is the first large N study of all registered INGOs and expands the time frame to the five years enforcement of the ONGO Law, providing insights for both scholars and practitioners on how the operational space of INGOs varies by issue areas and factors such as local connections.
